\documentclass[a4paper,10pt]{article}
\usepackage{config/config-eng} % Carga toda tu configuración profesional

\begin{document}
\pagestyle{empty} 

% HEADER
\begin{center}
    {\Huge \scshape{\color{primaryColor}Victoria Guarnieri}} \\ [5pt]
    {\Large {Biomedical Engineer}} \\ [8pt]
    \small
    \href{mailto:vickyguarnieri1@gmail.com}{\faEnvelope \ vickyguarnieri1@gmail.com} \ $|$ \ 
    \href{tel:+5491130410475}{\faPhone \ +54 9 11 3041-0475} \ $|$ \ 
    \faMapMarker* \ Buenos Aires, Argentina \\ [3pt]
    \href{https://github.com/vickyguar}{\faGithub \ vickyguar} \ $|$ \ 
    \href{https://linkedin.com/in/victoria-guarnieri-}{\faLinkedin \ victoria-guarnieri-} \ $|$ \ 
    \faIdCard \ DNI 43.660.111
\end{center}

% FORMACIÓN ACADÉMICA
\section{Education}
\begin{formacion}{Biomedical Engineering}{Facultad de Ingeniería y Ciencias Exactas y Naturales}{Universidad Favaloro (FICEN-UF)}{Mar 2020 -- Dec 2025}
    \item \textbf{GPA:} 8.35/10.
    \item \textbf{Final Degree Project:} Data Management in Oncology Research: Development of Integrated Software for \textit{In Vivo} Trials.
\end{formacion}
\tecnologias{Python, C/C++, C\#, MATLAB, SQL.} \\
\habilidades{Teamwork, problem solving, discipline, perseverance.}

% EXPERIENCIA LABORAL
\section{Work Experience}
\begin{experiencia}{Programa de Inteligencia Artificial en Salud, Hospital Italiano de Buenos Aires}
    \begin{rol}{AI Trainee}{Sep 2024 -- Present}
        \item Developed and validated a deep learning model for medical image classification.
        \item Design and execution of an interobserver agreement study to define training labels.
        \item Technical documentation and experiment tracking.
        \item Evaluation of external products.
    \end{rol}
\end{experiencia}
% \tecnologiasItems{
%     \item \textbf{Python 3.13:} PyTorch, Pandas, Numpy, Scikit-learn, Matplotlib, Seaborn. \textbf{R 4.3:} tidyverse, ggplot2, plotly, irrCAC.
%     \item \textbf{Cloud:} AWS SageMaker and AWS S3.
%     \item \textbf{Version control:} Git, Github and Bitbucket.
%     \item \textbf{Experiment tracking:} Weights \& Biases (wandb).
% }
% \habilidades{Data analysis and visualization, machine learning, deep learning, image processing, applied statistics.}
\tecnologias{\textbf{Python 3.13} (PyTorch, Pandas, Numpy, Scikit-learn, Matplotlib, Seaborn, Pyplot); \textbf{AWS services} (AWS SageMaker, S3); \textbf{version control} with Git, Github, Bitbucket; \textbf{experiment tracking} with Weights \& Biases (wandb); \textbf{R 4.3} (tidyverse, ggplot2, plotly, irrCAC).}\\
\habilidades{Data analysis and visualization, machine learning, deep learning, image processing, applied statistics.}

\vspace{6pt}
\begin{experiencia}{FICEN-UF -- Department of Mathematics}
    % \begin{rol}{Head of Practical Assigments}{Mar 2026 -- Present}
    %     \item In the subject \textbf{Cálculo III} (complex variable Calculus).
    %     \item Teaching of theoretical-practical classes.
    %     \item Development of study materials and exercise guides.
    %     \item Writing, evaluation and correction of exams.
    % \end{rol}
    \begin{rol_corto}{Student Assistant}{Aug 2021 -- Present}
        Assistant in the subjects \textbf{Calculus I} (single-variable calculus), \textbf{Calculus II} (multivariable calculus) and \textbf{Calculus III} (complex analysis).
    \end{rol_corto}
\end{experiencia}

\vspace{6pt}
\begin{experiencia}{FICEN-UF -- Department of Informatics}
    \begin{rol}{Student Assistant}{Mar 2025 -- Jul 2025}
        \item Assistant in the subject \textbf{Database}.
        \item Collaboration in the writing, evaluation and correction of partial exams and practical assignments, under supervision.
    \end{rol}
\end{experiencia}
\tecnologias{MySQL 8.0.} \\
\habilidades{Database modeling and normalization, SQL programming.}

\vspace{6pt}
\begin{experiencia}{Hospital Universitario Fundación Favaloro}
    \begin{rol}{Biomedical Engineering Intern}{May 2024 -- Sep 2024}
        \item Supervised professional practice.
        \item Preventive and corrective technical service tasks. Board-level and component-level repair; functionality control with biomedical testers; electrical safety control with analyzer; component purchase through the sector's fund.
        \item Update of protocols, in accordance with IRAM 15 standard and analysis of historical maintenance data.
    \end{rol}
\end{experiencia}
\tecnologias{Microsoft Excel, Neovero.} \\
\habilidades{Clinical Engineering.}

% CURSOS Y MINICURSOS
\section{Certifications}
\curso{Deep Learning: Neural Networks from Scratch}{Centro de e-Learning UTN FRBA. Graded.}{37}{Jul 2023}
\curso{Introduction to Unsupervised Machine Learning}{FICEN-UF}{16}{May 2023}
\curso{Machine Learning with Python}{Centro de e-Learning UTN FRBA. Graded.}{60}{May 2023}
\curso{Introduction to Python oriented to algorithms and competitive programming techniques}{IEEE UF, IEEE WIE y LambdaClass}{20}{Nov 2020}
% \curso{Modelos Aditivos Generalizados (GAM)}{Reunión del Grupo Argentino de Bioestadística}{4}{Octubre de 2025}
% \curso{Por qué (¿no?) me gustaría/quisiera/debería ``convertirme'' a la Estadística bayesiana y nunca me atreví a preguntármelo… }{Reunión del Grupo Argentino de Bioestadística}{3}{Octubre de 2025}
% \curso{Ideas estocásticas fundamentales que conectan el análisis exploratorio y la inferencia informal}{Reunión del Grupo Argentino de Bioestadística}{3}{Octubre de 2025}

% IDIOMAS Y SKILLS
\section{Language}
\textbf{English:} intermediate–advanced (technical reading and scientific writing).

% ASISTENCIA A CONGRESOS
\section{Conference Attendance}
\evento{XX Health Informatics Conference JIS Summit of Hospital Italiano de Buenos Aires}{Centro Metropolitano de Diseño, Ciudad Autónoma de Buenos Aires, Argentina. Hybrid event}{7 to 9 November 2025}
\evento{Update Workshop on Vulvar Pathology of the Iberoamerican Society of Vulva and Vagina (SIAVV)}{Yacht Club Puerto Madero, Ciudad Autónoma de Buenos Aires, Argentina}{24 October 2025}
\evento{XXV Argentinian Congress of Bioengineering, the XIV Clinical Engineering Conference and the III Latin American Conference on Clinical Engineering, SABI-2025}{Hotel 13 de Julio, Mar del Plata, Argentina}{14 to 17 October 2025}
\evento{XXIX Scientific Meeting of the Argentinian Group of Biostatistics, GAB 2025}{Universidad Nacional del Nordeste, Corrientes, Argentina}{1 to 3 October 2025}
\evento{II Statistics Teaching Conference}{Universidad Nacional del Nordeste, Corrientes, Argentina}{30 September 2025}
\evento{XVIII Health Informatics Conference JIS Summit of Hospital Italiano de Buenos Aires}{Centro Metropolitano de Diseño, Ciudad Autónoma de Buenos Aires, Argentina. Hybrid event}{1 to 3 November 2023}
\evento{XXIV Argentinian Congress of Bioengineering and the XIII Clinical Engineering Conference, SABI 2023}{Universidad Nacional de Arturo Jauretche, Florencio Varela, and Centro Cultural Kirchner, Ciudad Autónoma de Buenos Aires, Argentina}{3 to 6 October 2023}
\evento{XXIII Argentinian Congress of Bioengineering and the XII Clinical Engineering Conference, SABI 2022}{Universidad Nacional de San Juan, San Juan, Argentina}{13 to 16 September 2022}

% POSTERS
\section{Poster Presentations}
\evento{\normalsize{Determination of interobserver agreement degree for categorical variables: a case study}}{GAB 2025}{Rusconi Lagarrigue A.B., Sguiglia S., \textbf{Guarnieri V.}, et al}
\evento{\normalsize{Determination of the interobserver agreement degree in medical image segmentation: a case study}}{GAB 2025}{Sguiglia S., Rusconi Lagarrigue A.B., \textbf{Guarnieri V.}, et al}

% PRESENTACIONES ORALES
\section{Oral Presentations}
\evento{\normalsize{Interobserver agreement study in the assessment of pressure ulcer images}}{JIS SUMMIT 2025}{Rusconi Lagarrigue A.B., Sguiglia S., \textbf{Guarnieri V}}
\evento{\normalsize{Artificial Intelligence in medical practice}}{Jornada SIAVV}{Caridi J., \textbf{Guarnieri V}}

% BECAS Y RECONOCIMIENTOS
\section{Scholarships and Awards}
\begin{itemize}[leftmargin=1.2em, label=\small\faAward, nosep]
    \item \normalsize\textbf{Undergraduate Research Fellowship (BIE)}, UF \fecha{Feb 2022 -- Feb 2025}
    \item \normalsize\textbf{Second National Flag Escort (Honor Guard)} \small\textit{ - ranked 3rd highest GPA.}, FICEN-UF \fecha{Academic year 2024}
\end{itemize}

% VOLUNTARIADO 
\section{Volunteering}
\begin{experiencia}{Capítulo estudiantil de la Sociedad Argentina de Bioingeniería}
    \begin{rol}{Student Representative}{Mar 2024 -- Oct 2025}
        \item Project and event management.
        \item Communication and dissemination of technological and scientific events.
    %\item Fomento de la vinculación académica y profesional entre estudiantes de Bioingeniería a nivel nacional.
    \end{rol}
\end{experiencia}

\vfill
\begin{center}
    \footnotesize \color{black!50} Last updated: \today \
\end{center}

\end{document}